%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% In general, Cyrus writes "The only thing I can think of is removing sabbatical whenever
% a cover letter is required. Also if you're looking for a management position, possibly
% emphasize things that involve teamwork, project management, anything that would
% require social intelligence."


%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Wesley Spikes}
\address{3767 Clarington Ave, Apt 320 \\ Los Angeles, CA 90034}
\address{909.815.1079 \\ wesley.spikes@gmail.com}

\begin{document}

% \printdraftwatermark % DRAFT

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}
An accomplished software engineer and architect with a passion for leadership, security, systems, and mentoring. I seek out challenges as opportunities for growth, handle ambiguous situations well, and can break down complex problems into creative solutions with actionable tasks.

I am seeking a challenging senior technical or leadership role at a forward-thinking company.
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Perl, Bash, Python, Ruby, \LaTeX \\
Operating Systems & Linux (Debian, Ubuntu, Gentoo), OS X, Windows \\
Software & Apache, Chef, Nginx, git, vim, MySQL, Jenkins, Gerrit, KVM \\
Concepts & Application Security, CI/CD, Systems Configuration
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

% NB: Verb tense in this section is mostly present tense, since it's current events,
% with the exception of the personal lab, since it's completed and working.

\begin{rSubsection}{Sabbatical}{Sep 2016 - Present}{}{}
\item Successfully achieved many of the goals personally set at DreamHost; took a six-month sabbatical.
\item Learning C\# and Unity to mentor someone new to development.
\item Set up a personal lab within home office including four physical servers.
\item Reverse engineering software and embedded firmware.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{DreamHost}{Oct 2014 - Aug 2016}{Senior/Lead Software Engineer}{Los Angeles, CA}
\item Managed two direct reports.
\item Coordinated with other teams including Systems Engineering, Security, Support, and Corporate IT.
\item Managed core development infrastructure, including Gerrit and Jenkins.
\item Entrusted with various sets of secure credentials. Primary maintainer of deployed credentials.
\item Post-exploit incident response.
\item Modernized deployment of the primary codebase and its dependencies (fully documented), cutting deployment time down from 20 minutes to around 45 seconds.
\item Technical and architectural lead on the DreamPress 2, VPS-SSD, and Malware Remover projects.
\item Very active in internal bug bounty program; reported several notable issues.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{DreamHost}{Jan 2011 - Oct 2014}{Software Engineer}{Los Angeles, CA}
\item Configuration management using both Chef and in-house systems.
\item Projects included the launch of mod\_pagespeed (beat competitors to market) and the transition from subversion to git (including documentation and internal support).
\item Major contributions to the foundations/core of an old codebase (1997), without breaking production.
\item Notable contributions to the billing systems, thereby improving its resilience and extensibility.
\item Created detailed documented how the fraud detection systems worked.
\item Researched and documented many obscure settings and flags of the systems.
\item Fixed multiple security issues in the codebase.
\item Introduced CI processes from end-to-end, including: initial research/prototyping, getting buy-in, \\ implementation, training, and supporting the new system.
% ^ Forced line wrap to avoid "im-{\n}plementation", which looked weird to me.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{DreamHost}{Nov 2009 - Jan 2011}{Technical Support}{Los Angeles, CA}
\item Specialized in resolving complex, ongoing problems where it was difficult to find the root cause.
\item Diagnosed abnormally high load systems and troubleshot customer websites.
\item Configured systems - Linux-VServer, DNS, Apache, Nginx, users, and PHP.
\item Maintained a 99\% customer satisfaction rate.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Page Provider}{Dec 2006 - Nov 2009}{Systems Administrator}{Rancho Cucamonga, CA}
\item Startup hosting provider.
\item Built and deployed custom kernels and software for colocated customers.
\item Provisioned and deployed servers and services.
\item Configured and managed Apache, users, and databases.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
